---
title: '**Using knitr with Multilevel Models and Decision Support Trees**'
author: '**Som B. Bohora**'
job: CCAN
date: "February 03, 2015"
output: beamer_presentation
---

# **Outline**
  - `Markdown` & `R Markdown` (brief)
  - `knitr` in brief
  - `knitr` and `R Markdown` with RStudio options
  - Demonstration 
  
# **Markdown & R Markdown (very brief)**

##    **Markdown**
- It is a particular type of markup language (simple formatting syntax for authoring HTML, PDF, and MS Word documents from plain text format). 
- For example, ***LaTeX*** which is restricted to only PDF output & has greater learning curve

- Other tools such as **Pandoc** to render markdown document to other formats (HTML/Word/PDF)

- [THERE ARE WAYS AROUND, BUT ??](http://www.telegraph.co.uk/news/newsvideo/7207781/Daring-man-saves-van-from-train-crash.html)

# **Markdown & R Markdown (very brief) contd.** 
##   **R Markdown**

- It is a file format for making dynamic documents with R with `rmarkdown` package. 
- R Markdown document is written in markdown and enables execution of embedded R code chunks
- `rmarkdown` comes with the RStudio IDE
- `rmarkdown` and `pandoc` can be used outside of RStudio too. For e.g., rmarkdown::render()

# **R Markdown Basics**

```{r echo=FALSE, fig.width=7, fig.height=5}
library(png)
library(grid)
img <- readPNG("./SCUG Presentation/Trial/Final Presentation/pic2.png")
grid.raster(img)
```
    
# **knitr for reproducible research (author:Dr. Yihui Xie)**

##         **knitr + markdown + pandoc = rmarkdown**

- [COOL R MARKDOWN & knitr](https://www.youtube.com/watch?v=En_8UgGZXio)
- `knitr` is a package for producing reproducible documents and reports
- Code and text can be embeded
- Runs R code and includes the output (`knit` function from `knitr` package)
- `knitr` and `pandoc` used to work separately  


# **knitr and R Markdown wth RStudio**
## knitr code chunk options

Here is an example of knitr code chunk in .Rmd;

```{r echo=FALSE, message=FALSE, fig.width=2, fig.height=0.50}
library(png)
library(grid)
img <- readPNG("./SCUG Presentation/Trial/Final Presentation/pic1.png")
grid.raster(img)
```
    
- echo: show codes?
- eval: evaluate?
- warning/message/error: show/stop?
- results: markup/hide/asis?
- tidy: reformat codes?
- cache: cache results?
- fig.width and fig.height: figure options
- include: chunk results in the output?


# **Resources**

1. [knitr reference card](http://cran.r-project.org/web/packages/knitr/vignettes/knitr-refcard.pdf)
2. [R markdown and knitr cheatsheet](http://rmarkdown.rstudio.com/RMarkdownCheatSheet.pdf)
3. [R markdown webpage](http://rmarkdown.rstudio.com)
4. [Using R markdown](https://support.rstudio.com/hc/en-us/articles/200552086-Using-R-Markdown) 
5. [A similar approach that uses an R file underneath the Rmd file (discussed in May)](https://github.com/wibeasley/RAnalysisSkeleton/tree/master/Analyses/Report1)

```{r echo=FALSE, message=FALSE, fig.width=4, fig.height=2.5, fig.align='left'}
library(png)
library(grid)
img1 <- readPNG("./SCUG Presentation/Trial/Final Presentation/knitrbook.png")

grid.raster(img1)
```

# **Let's see some demonstrations**


