---
title: "Using knitr with Multilevel Models and Decision Support Trees"
author: "Som Bohora"
date: "Febeuary 03, 2015"
output: pdf_document
geometry: margin = 0.3cm
---

```{r echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}
rm(list=ls(all=TRUE))
library(foreign)
library(reshape2)
library(sqldf)
library(reshape)
library(Hmisc)
```

## Reading data and manipulation
```{r, echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE, comment=' ', tidy=TRUE}
depressData <- read.csv("./SCUG Presentation/Final Presentation/Final/Demonstration/Data/data1.csv", header=TRUE) 

depressData$CM <- with(depressData, ifelse(hurt1w1 %in% c(1,2,3,4) | badnamesw1 %in% 1:4 | needsw1 %in% 1:4 | 
                              sexabusew1 == 1, CM <- 1, ifelse(hurt1w1  == 0 & badnamesw1 == 0 & needsw1 == 0 
                              & sexabusew1 == 0, CM <- 0, NA))) 

depressData$hurt1w1 <- depressData$badnamesw1 <- depressData$needsw1<-depressData$sexabusew1<-NULL
names(depressData)

catVars <- names(depressData) %in% c("Group", "CM","singpsyrw1", "singpsyrw2", "singpsyrw3","pregw1", "pregw2",
                                    "pregw3","helpfw1", "helpfw2", "helpfw3","depresw1", "depresw2", "depresw3")

allFactorVars <- data.frame(depressData[!catVars], sapply(depressData[catVars], function(x) as.factor(x)))

numVars <- !names(allFactorVars) %in% c("Group","CM","singpsyrw1", "singpsyrw2", "singpsyrw3","pregw1", "pregw2",
                                      "pregw3","helpfw1", "helpfw2", "helpfw3", "depresw1", "depresw2", "depresw3")

allNumericFactorVars <- data.frame(allFactorVars[!numVars], 
                                   sapply(allFactorVars[numVars], function(x) as.numeric(x)))
```

## Imputation and restructure
```{r, echo = TRUE, message=FALSE, results='hide', eval=TRUE, comment=' '}
library(mice)
imputed1 <- mice(allNumericFactorVars, me =c("", "logreg","logreg","logreg","logreg","logreg","logreg",
                                             "logreg","logreg","logreg","logreg","","","", "",
                                             "norm","norm","norm","norm","norm","norm","norm","norm","norm"))

# Removing these variables as predictors
pred <- imputed1$pred
pred[,c("ID","Group", "bdiw1", "bdiw2", "bdiw3")] <- 0

# Removing `pred` variables as predictors and re-running `MICE`
imputed2 <- mice(allNumericFactorVars, seed= 98765431, me =c("", "logreg","logreg","logreg","logreg","logreg",
                                  "logreg","logreg","logreg","logreg","logreg","","","", "","norm","norm","norm",
                                  "norm","norm","norm","norm","norm","norm"), pred = pred)

completeImputed <- complete(imputed2, inc=FALSE)

long <-reshape(completeImputed, varying =list(c("bdiw1","bdiw2", "bdiw3"), 
                                         c("PHASTcw1","PHASTcw2","PHASTcw3"),
                                         c("singpsyrw1", "singpsyrw2", "singpsyrw3"),
                                         c("TOTFRSw1", "TOTFRSw2", "TOTFRSw3"),
                                         c("pregw1", "pregw2", "pregw3"),
                                         c("helpfw1", "helpfw2", "helpfw3"),
                                         c("spstotw1","spstotw2","spstotw3")),
#                                          c("datew1","datew2","datew3")),
                  v.names=c("bdiScore", "IPV", "relationship", "famRes", "preg", "depressMed", "socialSupport"), 
                        times = 1:3, new.row.names = NULL, direction = "long")

keepLong <- subset(long, 
            select = c(ID, Group,CM, time,bdiScore,IPV,relationship,famRes,preg,depressMed,socialSupport))
nrow(keepLong)

keepLong[order(keepLong$time),]

nrow(depressData[complete.cases(keepLong),])

isComplete <- complete.cases(keepLong)
sum(isComplete)
finalLong <- keepLong[isComplete,]
nrow(finalLong)

tapply(finalLong$IPV, finalLong$time, summary)
summary(finalLong$IPV)
```

<!-- Use of inline R codes in the R Markdown. -->

The mean of `IPV` is `r mean(finalLong$IPV, na.rm=TRUE)` and correlation between IPV and depression is `r with(finalLong, cor(IPV, bdiScore))` which is less than `r 0.5 - (0.2*0.03)`.

## Regression tree on IPV
Regression tree on IPV;
```{r, echo=TRUE, message=FALSE, fig.width=2.7, fig.height=3, comment=' '}
library(rpart)
library(party)
library(partykit)
library(rpart.plot)

name1 <- c("bdiw1","bdiw2","bdiw3")
name2 <- c("PHASTcw1", "PHASTcw2", "PHASTcw3")

forReg <- depressData[, c("bdiw1", "PHASTcw1")]

reglist1 <- list()

for (i in 1:3){
  reg1 <- paste(name1[i],name2[i], sep='~')
#   print(regress)
  reglist1[[i]] <- rpart(as.formula(reg1), maxdepth=2, method ='anova', data=completeImputed)
  plots1 <- plot(as.party(reglist1[[i]]),tp_args = list(id = FALSE))
}

with(finalLong,tapply(IPV,time,summary))
```

## Categorizing IPV based on regression tree cut-off
```{r, echo= TRUE, message=FALSE, eval=TRUE}
library(lme4)
library(MASS)
library(lmerTest)
library(nlme)
library(plyr)

finalLong$IPVCat <- ifelse(finalLong$IPV < 1.115, 0, 1)
table(finalLong$IPVCat)

# finalLong <- ddply(finalLong, "time", function(x) {within(x, {
#               if (time[1] == '1') {
#             IPVCat <- ifelse(IPV < 1.5, 0, 1)
#             
#             } else if (time[1] == '2') {
#             IPVCat <- ifelse(IPV < 2.5, 0, 1)
#             
#            } else {
#             IPVCat <- ifelse(IPV < 47.5, 0, 1)      
#           }})
#       })
# 
# #finalLong[,c("time","IPV", "IPVCat")]
finalLong$IPVCat <- as.factor(finalLong$IPVCat)
```

## Different mixed-effects models (linear and quadratic) with IPV as categorical predictor
Results from linear mixed-effects model;

```{r, echo=TRUE, message=FALSE, warning=FALSE, comment=' '}
library(lme4)
library(lmerTest)
library(gridExtra)
library(coefplot)

mixedModel1 <- lmer(bdiScore ~ Group*factor(time) + CM*factor(time) + IPVCat + socialSupport + 
                IPVCat:socialSupport + relationship + famRes + IPVCat:famRes + preg + depressMed +
                (1 | ID), data = finalLong)

anova(mixedModel1, ddf ="Kenward-Roger")

p1 <- plot(mixedModel1,id=0.05,idLabels=~.obs)
p2 <- plot(mixedModel1,ylim=c(-1.5,1),type=c("p","smooth"))
p3 <- plot(mixedModel1,col=finalLong$bdiScore)
p4 <- plot(mixedModel1,bdiScore~resid(.))
p5 <- coefplot(mixedModel1)
re<-ranef(mixedModel1,condVar = TRUE)
p6 <- qqmath(~re[[1]])
# p1; p2; p3; p4;p4;p5;p6
# Some regression diagnostics 
grid.arrange(p1,p2,nrow=1)
grid.arrange(p3,p4,nrow=1)
grid.arrange(p5,p6,nrow=1)
```