---
title: P4 Survey Validation     # Change this value for new validators.
output:
  html_document:
    keep_md: yes
    toc: yes
---

This report identifies violations in the [P4 Community Survey](https://bbmc.ouhsc.edu/redcap/redcap_v6.11.5/index.php?pid=302) dataset.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of three directories.-->
```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
# Change this value for new validators.
opts_knit$set(root.dir='./../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results    = 'show',
  comment    = NA,
  tidy       = FALSE,
  fig.width  = 6.5,
  fig.height = 4,
  fig.path   = 'figure-png/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echo_chunks <- FALSE
options(width=100) #So the output is 25% wider than the default.

# Change this value for new validators.
read_chunk("./analysis/survey-validation/survey-validation.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. -->
```{r load-sources, echo=echo_chunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. -->
```{r load-packages, echo=echo_chunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. -->
```{r declare-globals, echo=echo_chunks, results='show', message=FALSE}
```


<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r, echo=echo_chunks, message=FALSE}
  #Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=TRUE}
```

# Instructions

1. Work through each line in the table to discover & correct entry mistakes in the database.  Be aware that a single mistake may manifest in multiple rows; fixing one value may clear several rows.
1. Click the `record id` value in a row to be taken to the participant's Event Grid in REDCap (ie, the 'stop light page').
1. Document your manual corrections to the records are documented in `r path_output`.  Be careful not to move this file to somewhere unsafe.
1. To help discover the dataflow and problematic location, use the
    * project's [codebook](https://bbmc.ouhsc.edu/redcap/redcap_v6.11.5/Design/data_dictionary_codebook.php?pid=302) in REDCap,
    * [survey-ferry.R](https://github.com/OuhscBbmc/P4/blob/master/manipulation/ferry/survey-ferry.R) file, and
    * [survey-validation](https://github.com/OuhscBbmc/P4/tree/master/analysis/survey-validation) report.
1. If you create a new check, make sure the error message won't reveal any PHI.


# Assemble Checks
```{r assemble-checks, echo=echo_chunks, message=TRUE, results='asis'}
```

# Execute Checks
```{r execute-checks, echo=echo_chunks, message=TRUE}
```

# Display Table
```{r display-table, echo=echo_chunks, message=TRUE}
```


# Save To Disk
```{r verify-values, echo=echo_chunks, message=TRUE}
```

```{r specify-columns-to-upload, echo=echo_chunks, message=TRUE}
```

```{r save-to-disk, echo=echo_chunks, message=TRUE}
```


# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session-info, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"), "in", report_render_duration_in_seconds, "seconds." )
sessionInfo()
```
